Online {\IterComp}

### 2017-10-19 abstract.tex
minor reviews in abstract

    Iterative compilation can dramatically improve the performance of a program by searching for the best optimization.
    However, it relies upon repeatedly evaluating optimizations on predefined representative inputs.
    If the developers fail to guess what is a representative input or usage patterns change over time,
    then the wrong optimizations may be selected.
    Searching the optimization space with actual user inputs, during deployment, has previously seemed infeasible.
    Program side effects and difficulties capturing the system state mean that any given input can
    only be executed once. %Since each input may entail a different amount of work, the search cannot use runtime to compare
    %optimizations, and there is no baseline against which to define speedup.
    Unless we find a way to compare optimizations even when inputs are executed only once, we will be unable to use real user
    input for iterative compilation, users will not have the best optimized programs, and performance will suffer.

>>>>

    Iterative compilation can dramatically improve the performance of a program by searching for the best optimization.
    However, it relies upon repeatedly evaluating optimizations on predefined representative inputs.
    If the developers fail to guess what is a representative input or usage patterns change over time,
    then the wrong optimizations may be selected.
    Searching the optimization space with actual user inputs, during deployment, has previously seemed infeasible.
    Program side effects and difficulties capturing the system state mean that any given input can
    only be executed once. %Since each input may entail a different amount of work, the search cannot use runtime to compare
    %optimizations, and there is no baseline against which to define speedup.
    Unless we find a way to compare optimizations even when inputs are restricted to execute only once, we will be unable to apply 
    iterative compilation in online scenarios with real user inputs, users will not have the best optimized programs, and performance will suffer.
